\huge Tor's Usability for Censorship Circumvention

### 2016-04-23 pets2017-paper/pets2017-paper.tex
Give a year for the 3.5 UI overhaul.

There have been been no published usability evaluations of
Tor Browser since the 3.5 series, which introduced radical UI changes~\cite{torbrowser-35}.
The most recent usability effort is an unpublished pilot study by Lee and Fifield~\cite{uxsprint} 
that tested the downloading, installation, and browsing tasks in Tor Browser.  This study uncovered a number of issues~\cite{uxsprint2015-tickets},
some of which influenced changes in Tor Browser version~4.5 and later.

>>>>

There have been been no published usability evaluations of
Tor Browser since the release of the 3.5 series in 2013, which introduced radical UI changes~\cite{torbrowser-35}.
The most recent usability effort is an unpublished pilot study by Lee and Fifield~\cite{uxsprint} 
that tested the downloading, installation, and browsing tasks in Tor Browser.  This study uncovered a number of issues~\cite{uxsprint2015-tickets},
some of which influenced changes in Tor Browser version~4.5 and later.
